Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-29 GEMDataSource.Rmd
All data included

@@

# Run linear regression R1
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)

@@

# Run linear regression R2
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)

@@

# Run linear regression R3
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)

>>>>

# Import tempfix for GEM data (created this by copying data frame, editing outide R, and saving .csv in repository)

GEMAnnualData <- repmis::source_data("https://github.com/SamDund/Assign2Education/raw/master/GEMData/Gemyears.csv", header = TRUE, cache = FALSE)

##### Clean and merge tempfix GEM Data ####

# Change column names
names(GEMAnnualData) <- gsub("Year01", "2001", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year02", "2002", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year03", "2003", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year04", "2004", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year05", "2005", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year06", "2006", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year07", "2007", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year08", "2008", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year09", "2009", names(GEMAnnualData))
names(GEMAnnualData) <- gsub("Year10", "2010", names(GEMAnnualData))

# Change years from columns to rows and create CleanGEM
CleanGEM <- melt(data = GEMAnnualData,
                 id.vars = c("Country"),
                 measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Rename columns
CleanGEM <- plyr::rename(x = CleanGEM,
                         replace = c("variable" = "Year",
                                     "value" = "WayofTeach"))

# Merge Clean CleanGEM with FinalGEM 
CompleteData <- merge(CleanGEM, FinalGEM,
                   union("Country", "Year"),
                   all = TRUE)

@@

# Run linear regression R1
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)

@@

# Run linear regression R2
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)

@@

# Run linear regression R3
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + lm(WayofTeach) + Country, data = CompleteData)
